Typing a linear \picalc

### 2020-04-24 paper/paper.tex
Update substitution diagram

\begin{figure}[ht]
  \begin{subfigure}{.5\textwidth}
  \centering
  \begin{tikzpicture}
    \node (gamma) at (0,2) {$\Gamma$};
    \node (psi-m) at (4,2) {$\Psi_m$};
    \node (psi-l) at (4,4) {$\Psi_l$};
    \node (psi-r) at (4,0) {$\Psi_r$};
    \draw[->]                (gamma) -- node[above,sloped] {$\Delta$} node[below] {$\Delta_i = \ell_{\o}$} (psi-m);
    \draw[->]                (gamma) -- node[above,sloped] {$\vdash P$}               (psi-l);
    \draw[->,densely dotted] (gamma) -- node[below,sloped] {$\vdash \subst{P}{j}{i}$} (psi-r);
    \draw[->]                (psi-m) -- node[right]        {$m@i$}                    (psi-l);
    \draw[->]                (psi-m) -- node[right]        {$m@j$}                    (psi-r);
  \end{tikzpicture}
  \caption{Diagrammatic representation of the generalized substitution theorem.}
  \label{fig:subst}
  \end{subfigure}
  % Do not leave empty line
  \begin{subfigure}{.5\textwidth}
  \centering
  \begin{tikzpicture}
    \node (gamma) at (0,2) {$\Gamma$};
    \node (xi-l)  at (0,4) {$\Xi_l$};
    \node (xi-r)  at (0,0) {$\Xi_r$};
    \node (psi-m) at (4,2) {$\Psi_m$};
    \node (psi-l) at (4,4) {$\Psi_l$};
    \node (psi-r) at (4,0) {$\Psi_r$};
    \draw[->]                (gamma) -- node[above,sloped] {$\Delta$} node[below] {$\Delta_i = \ell_{\o}$} (psi-m);
    \draw[->]                (gamma) -- node[left]         {$\ell_i@i$}               (xi-l);
    \draw[->,densely dotted] (gamma) -- node[left]         {$\ell_i@j$}               (xi-r);
    \draw[->]                (xi-l)  -- node[above]        {$\vdash P$}               (psi-l);
    \draw[->,densely dotted] (xi-r)  -- node[above]        {$\vdash \subst{P}{j}{i}$} (psi-r);
    \draw[->]                (psi-m) -- node[right]        {$m@i$}                    (psi-l);
    \draw[->]                (psi-m) -- node[right]        {$m@j$}                    (psi-r);
  \end{tikzpicture}
  \caption{
    Diagrammatic representation of the generalized substitution for process input.
    Thanks to the additional premise in Remark \ref{re:delta-zero}, we know that $m$ is at least capable of $\ell_i$, i.e. $\opsquared{m}{\delta}{\ell_i}$ for some $\delta$.
  }
  \label{fig:subst-input}
  \end{subfigure}
\end{figure}

>>>>

\begin{figure}[h]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}
      \node (gamma-l) at (0,6)   {$\Gamma_l$};
      \node (gamma-m)   at (0,3)   {$\Gamma$};
      \node (gamma-r) at (0,0)   {$\Gamma_r$};
      \node (xi-l)    at (3,5.5) {$\Xi_l$};
      \node (theta)   at (3,3.3) {$\Theta$};
      \node (delta-m) at (3,2.7) {};
      \node (xi-r)    at (3,0.5) {$\Xi_r$};
      \node (psi-l)   at (6,5)   {$\Psi_l$};
      \node (psi-m)   at (6,3)   {$\Psi$};
      \node (psi-r)   at (6,1)   {$\Psi_r$};

      \draw[-]  (gamma-m) -- (delta-m.center);
      \draw[->] (delta-m.center) -- node[align=center,below] {$\Delta$\\$\Delta_i = \ell_{\o}$}(psi-m);

      \draw[->,densely dotted] (gamma-m) -- (theta);
      \draw[->,densely dotted] (theta) -- (psi-m);

      \draw[->] (gamma-l) -- node[left] {$\ni_i m$} (gamma-m);
      \draw[->] (gamma-r) -- node[left] {$\ni_j m$} (gamma-m);
      \draw[->] (psi-l) -- node[right] {$\ni_i n$} (psi-m);
      \draw[->] (psi-r) -- node[right] {$\ni_j n$} (psi-m);

      \draw[->] (gamma-l) -- node[above] {$\vdash P$} (xi-l);
      \draw[->] (xi-l) -- node[above] {$\vdash Q$} (psi-l);
      \draw[->,densely dotted] (gamma-r) -- node[below] {$\vdash \subst{P}{j}{i}$} (xi-r);
      \draw[->,densely dotted] (xi-r) -- node[below] {$\vdash \subst{Q}{j}{i}$} (psi-r);
      \draw[->,densely dotted] (xi-l) -- node[left] {$\ni_i l$} (theta);
      \draw[->,densely dotted] (xi-r) -- node[left] {$\ni_j l$} (theta);
    \end{tikzpicture}
    \caption{
      Diagrammatic representation of the generalized substitution for process input.
      Thanks to the additional premise in Remark \ref{re:delta-zero}, we know that $m$ is at least capable of $n$, i.e. $\opsquared{m}{\delta}{n}$ for some $\delta$.
    }
    \label{fig:subst}
  \end{subfigure}
  \hspace{\fill} % DO NOT LEAVE EMPTY LINE
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tikzpicture}
      \node (gamma-l) at (0,4)   {};
      \node (gamma-m) at (0,2)   {};
      \node (gamma-r) at (0,0)   {};
      \node (xi-l)    at (2,5)   {};
      \node (xi-m)    at (2,3.5) {};
      \node (xi-r)    at (2,2)   {};
      \node (psi-m)   at (4,3.5) {};

      \draw[->] (gamma-l) -- (xi-r);
      \draw[->] (gamma-m) -- (xi-r);
      \draw[->] (gamma-r) -- (xi-r);
      \draw[->] (gamma-l) -- (gamma-m);
      \draw[->] (gamma-r) -- (gamma-m);
      \draw[->] (xi-l)    -- (xi-m);
      \draw[->] (xi-r)    -- (xi-m);
      \draw[->] (xi-l)    -- (psi-m);
      \draw[->] (xi-m)    -- (psi-m);
      \draw[->] (xi-r)    -- (psi-m);
    \end{tikzpicture}
    \caption{
      Alternative approach without the $\ni_i n$ and $\ni_j n$ arrows.
      These are not strictly necessary, but they make the inductive hypotheses compositional.
      Without them, framing lemmas would have to be used extensively.
    }
    \label{fig:subst-compositionality}
  \end{subfigure}
\end{figure}
